Extracting sunbeams from cucumbers: Computational reproducibility is essential for archaeological science

### 2025-02-15 README.Rmd
dockerfile and instructions

## How to run in your browser or download and run locally

This research compendium has been developed using the statistical
programming language R. To work with the compendium, you will need
installed on your computer the [R
software](https://cloud.r-project.org/) itself and optionally [RStudio
Desktop](https://rstudio.com/products/rstudio/download/).

You can download the compendium as a zip from from this URL:
[master.zip](/archive/master.zip). After unzipping:

-   open the `.Rproj` file in RStudio\
-   install the packages used in the Quarto document\
-   finally, render the `analysis/paper/paper.qmd` document to produce the `paper.docx`, or run `rmarkdown::render("analysis/paper/paper.qmd")` in the R console

>>>>

## How to download and run locally in a Docker container

This research compendium includes a [Dockerfile](Dockerfile) that specifies the computational environment used to generate the results presented in the paper. You can recreate this environment, which includes R, RStudio and all necessary R packages, on your computer by following these steps:

1. Install [Docker](https://www.docker.com/get-started/) on your computer 
2. Download the compendium as a zip from from this URL:
[master.zip](/archive/master.zip) and unzip    
3. Set your terminal working directory to the compendium, and run `docker build -t wos .` to build the container on your computer, it will take a few minutes and require an internet connection.
4. Run in your terminal `docker run --rm -it -e ROOT=TRUE -e PASSWORD=rstudio -dp 8787:8787 wos` to run the container
5. Go to http://localhost:8787/ with your browser and enter rstudio in both fields to start RStudio in the browser, running in the Docker container
6. In RStudio, run `rstudioapi::openProject("/home/rstudio/web-of-science-archaeology")` to open this project
7. Run `rmarkdown::render("analysis/paper/paper.qmd")` to render the Quarto document
8. When finished, to remove the Docker container and files, run this in the terminal `docker ps -aq | xargs docker stop | xargs docker rm`
